### 2022-05-29 README.Rmd
replace http with https

[![R build status](https://github.com/slu-openGIS/areal/workflows/R-CMD-check/badge.svg)](https://github.com/slu-openGIS/areal/actions)
[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=main)
[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
[![Downloads](http://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](http://www.r-pkg.org/pkg/areal)
[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
[![DOI](http://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)

@@

### *Joural of Open Souce Software* Article
An [article](http://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](http://joss.theoj.org/). The article includes benchmarking of `areal` performance on several data sets. Please [cite the paper](/inst/CITATION) if you use `areal` in your work!

>>>>

[![R build status](https://github.com/slu-openGIS/areal/workflows/R-CMD-check/badge.svg)](https://github.com/slu-openGIS/areal/actions)
[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=main)
[![CRAN_status_badge](https://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
[![cran checks](https://cranchecks.info/badges/worst/areal)](https://cran.r-project.org/web/checks/check_results_areal.html)
[![Downloads](https://cranlogs.r-pkg.org/badges/areal?color=brightgreen)](https://www.r-pkg.org/pkg/areal)
[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647) 
[![DOI](https://joss.theoj.org/papers/10.21105/joss.01221/status.svg)](https://doi.org/10.21105/joss.01221)

@@

### *Joural of Open Souce Software* Article
An [article](https://joss.theoj.org/papers/10.21105/joss.01221) describing `areal`'s approach to areal weighted interpolation has been published in the [*The Journal of Open Source Software*](https://joss.theoj.org/). The article includes benchmarking of `areal` performance on several data sets. Please [cite the paper](/inst/CITATION) if you use `areal` in your work!
